### 2010-10-19 docs/FAQ/faq.tex
add some recent stuff

@@

@@

>>>>

  The tolerances used for the various multigrid solves in the code
  can be overridden on a problem-by-problem basis by putting a
  copy of {\tt MAESTRO/Source/mg\_eps.f90} into the problem directory
  and resetting the tolerances.  The role of each of these tolerances
  is described in {\tt MAESTRO/docs/mg/}.

@@

\item {\em Why is $\gammabar$ computed as the average of the full state
       $\Gamma_1$ instead of computed from the base state density and 
       pressure via the equation of state?}

 The primary reason is that there is no base state composition.  The
 base state density is simply the average of the full state density,
 and the base state pressure is the pressure required for hydrostatic
 equilibrium.  There is no thermodynamic relationship enforced between
 these base state quantities.

\item {\em Can I run a full star in 2-d axisymmetric geometry?}

 No.  This is a design decision.  There is no support for axisymmetric
 coordinates in MAESTRO.  Spherical problems must be run in 3-d.

@@

\section{Analysis}

\item {\em I want to open a plotfile, derive a new quantity from
 the data stored there, and write out a new plotfile with this derived 
 data.  How do I do this?}

 One implementation of this can be found in {\tt
   fParallel/data\_processing/tutorial/fwrite2d.f90}.  This reads in
 the plotfile data using the {\tt plotfile\_module} that the {\tt
   data\_processing} routines rely on, but then builds a multifab
   and writes the data out to a plotfile using the BoxLib write
   routines.
